Automated Analysis of Muscle X-ray Diffraction \\ Imaging with MCMC

### 2015-06-03 paper.tex
Swapped paper format to LNCS

\documentclass{sig-alternate}

\usepackage[usenames,dvipsnames]{color}
\usepackage{xspace}

\usepackage{fancyvrb}
\DefineVerbatimEnvironment{code}{Verbatim}{fontsize=\small}
\DefineVerbatimEnvironment{example}{Verbatim}{fontsize=\small}

% Looks better (and more concise) than Times New Roman
\usepackage{times}
% Better spacing
\usepackage{microtype}
\usepackage[normalem]{ulem}
\usepackage{enumitem}
% Caption package both lets you set the spacing between figure and caption
% and also makes the \figref{} point to the right place.
\usepackage[font=bf,aboveskip=0pt,belowskip=-12pt]{caption}
% Get the caption package to work with ACM style
\DeclareCaptionType[placement=b,within=none]{copyrightbox}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newfont{\mycrnotice}{ptmr8t at 7pt}
\newfont{\myconfname}{ptmri8t at 7pt}
\let\crnotice\mycrnotice%
\let\confname\myconfname%

\permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than the author(s) must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from Permissions@acm.org.}
\conferenceinfo{}{DMAH 2015, September 4th, Kohala Coast, USA}
\copyrightetc{}
\crdata{}

% Allow comments by name
\newcommand{\note}[2]{
    \textbf{\textcolor{#1}{#2}}
}
\newcommand{\comment}[1]{\note{red}{#1}}
\newcommand{\dave}[1]{\note{PineGreen}{Dave: #1}}
\newcommand{\magda}[1]{\note{Cyan}{Magda: #1}}
\newcommand{\tom}[1]{\note{OrangeRed}{Tom: #1}}

% To remove all notes, uncomment the next line.
%\renewcommand{\note}[2]{\unskip}

\newcommand{\ie}{{\em i.e.}\ }
\newcommand{\eg}{{\em e.g.}\ }
\newcommand{\ea}{{\em et al.}\xspace}
\newcommand{\aka}{{\em a.k.a.}\ }

\usepackage{url}
\usepackage[pdftex]{hyperref}

% Figures
\newcommand{\figureimgs}{
\begin{figure}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figures/x_ray_image_montage}
  \vspace{-12pt}
  \caption{\label{fig:imgs}
  	X-ray diffraction images.
    A) An X-ray diffraction image exhibits $d_{10}$, $d_{11}$, and
    $d_{20}$ peaks; the first and last are proportional to the
    distance between adjacent rows of thick filaments. B) In this
    image, two fibers at slight angles to each other have generated
    multiple $d_{10}$ peaks which must be segregated during the
    detection process.  
	}
	\vspace{-2pt}
\end{figure}
}

\newcommand{\figureworkflow}{
\begin{figure}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figures/img_analysis}
  \vspace{-8pt}
  \caption{\label{fig:workflow}
  	Analysis workflow.
    The blocked center region is detected and used as a landmark.  Low
    signal regions and edges are masked. The image is smoothed and
    peaks are detected, clustered, and classified. The background
    (sans that surrounding diffraction lines) is computed and
    subtracted. Regions of interest surrounding the $d_{10}$ peaks are
    extracted and the generating distributions are fit with an MCMC
    sampler. We marginalize across peak parameters other than those of
    interest.  
	}
	\vspace{-2pt}
\end{figure}
}

\begin{document}
\title{Automated Analysis of Muscle X-ray Diffraction \\ Imaging with MCMC}
\author{C.\ David Williams$^{1}$,  Magdalena Balazinska$^2$, Thomas Daniel$^1$ \\
\affaddr{$^1$Department of Biology, $^2$Department of Computer Science \& Engineering}\\
\affaddr{University of Washington} \\
}
\maketitle

% \dave{Presumably this gets filled in later?}
%    \vspace{-8pt}
%    \category{H.2.4}{Database Management}{Systems---Distributed databases, Query processing, Relational databases}
%    \vspace{-8pt}
%    \keywords{Myria; parallel data management; Cloud service; astronomy}

\sloppy

%%%%%%%%%%%
%\section{Questions addressed}
%\label{sec:addressed}

%In this work, we focus on the following questions:

%\begin{itemize}[noitemsep]
%\item Are sufficient conserved markers available in small-angle scattering diffraction images for automatic segmentation?
%\item Does MCMC distribution fitting provide reliable estimates of diffraction peak properties such as center and decay?
%\end{itemize}

@@

\begin{itemize}[noitemsep]
\item Development of a declarative language to describe processing
    steps will speed use of this technique and ease reproducibility.
    The key question is to define the types of operations that users
    should be able to specify and how to specify them. Our goal is to
    generalize to a broad set of analysis needs for X-ray images of
    muscle structure.
\item Packaging of this tool chain into a cloud deployable
    containerized image will enable trivial scaling to work with
    larger datasets. Furthermore, the ability to access to tool chain
    directly through a web browser with automatic back-end deployment
    of the analysis pipeline will facilitate adoption. 
\item Application of these techniques to coming ultra-high
    temporal-resolution images with far lower signal:noise will strain
    autosegmentation and peak-fitting techniques. 
\end{itemize}

>>>>

\documentclass{llncs}

\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Allow comments by name
\renewcommand{\note}[2]{\textbf{\textcolor{#1}{#2}}}
\newcommand{\comment}[1]{\note{red}{#1}}
\newcommand{\dave}[1]{\note{PineGreen}{Dave: #1}}
\newcommand{\magda}[1]{\note{Cyan}{Magda: #1}}
\newcommand{\tom}[1]{\note{OrangeRed}{Tom: #1}}
% To remove all notes, uncomment the next line.
%\renewcommand{\note}[2]{\unskip}

% Figures
\newcommand{\figureimgs}{
\begin{figure}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figures/x_ray_image_montage}
  \caption{\label{fig:imgs}
  	X-ray diffraction images.
    A) An X-ray diffraction image exhibits $d_{10}$, $d_{11}$, and
    $d_{20}$ peaks; the first and last are proportional to the
    distance between adjacent rows of thick filaments. B) In this
    image, two fibers at slight angles to each other have generated
    multiple $d_{10}$ peaks which must be segregated during the
    detection process.  
	}
	\vspace{-10pt}
\end{figure}
}

\newcommand{\figureworkflow}{
\begin{figure}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figures/img_analysis}
  \caption{\label{fig:workflow}
  	Analysis workflow.
    The blocked center region is detected and used as a landmark.  Low
    signal regions and edges are masked. The image is smoothed and
    peaks are detected, clustered, and classified. The background
    (sans that surrounding diffraction lines) is computed and
    subtracted. Regions of interest surrounding the $d_{10}$ peaks are
    extracted and the generating distributions are fit with an MCMC
    sampler. We marginalize across peak parameters other than those of
    interest.  
	}
	\vspace{-10pt}
\end{figure}
}

\begin{document}

%%%%%%%%%%%
\frontmatter
\pagestyle{headings}  % switches on printing of running heads
\addtocmark{MCMC Analysis of X-ray Diffraction Images} % additional mark in the TOC

%%%%%%%%%%%
\mainmatter
\title{Automated Analysis of Muscle X-ray Diffraction \\ Imaging with MCMC}
\author{C.\ David Williams\inst{1} \and Magdalena Balazinska\inst{1} \and Thomas Daniel\inst{1}}
\institute{Department of Biology, University of Washington, Seattle WA 98195, USA, \\
  \email{cdave@uw.edu}
  }
\maketitle

%%%%%%%%%%%
\begin{abstract}

  High-speed X-ray diffraction is the state-of-the-art approach to
  understanding protein structure and dynamics in living tissues,
  especially muscles.  Existing analytic approaches, however, require
  expert hand-digitization to extract parameters of interest. This
  produces repeatable measurements, but remains subjective and does
  not offer information on the precision of the measured parameters or
  strict reproducibility of analyzed data.  We developed a processing
  tool chain, which first segments the diffraction image into regions
  of interest using highly conserved features and then samples the
  possible parameter values with a Markov chain Monte Carlo approach.
  Our approach produces an automated, reproducible, objective estimate
  of relevant image parameters.
  \keywords{image analysis, X-ray diffraction, muscle structure, MCMC modeling}
\end{abstract}

@@

\begin{itemize}
\item Development of a declarative language to describe processing
    steps will speed use of this technique and ease reproducibility.
    The key question is to define the types of operations that users
    should be able to specify and how to specify them. Our goal is to
    generalize to a broad set of analysis needs for X-ray images of
    muscle structure.
\item Packaging of this tool chain into a cloud deployable
    containerized image will enable trivial scaling to work with
    larger datasets. Furthermore, the ability to access to tool chain
    directly through a web browser with automatic back-end deployment
    of the analysis pipeline will facilitate adoption. 
\item Application of these techniques to coming ultra-high
    temporal-resolution images with far lower signal:noise will strain
    autosegmentation and peak-fitting techniques. 
\end{itemize}
